A Comparison of Actor Critic and Policy Gradient \\ Algorithms for Learning Mechanical Designs

### 2022-04-28 Paper/PaperForReview.tex
added specified height data to paper

The RL algorithm was utilized to find designs for a single reward case. Time series data was captured during the simulation phase of training and was used to evaluate the designs performance through with this reward. The reward used was:
%
\begin{equation}
        \mathbb{R}_1 = \left (\textbf{X}  \right )_{\text{max}}
\end{equation}
% 
where $\textbf{X}$ was the timeseries rod height of the monopode captured during simulation. The goal of the first reward was to find a design that would cause the monopode to jump as high as possible.

@@

Figures~\ref{fig:spring_zeta_height} represents the height the monopode could reach for the design/action space. The design space provided represents a space where a wider range of damping ratios are allowed. This wider range of possible values makes it more likely that the agent will settle to a local maxima. Additionally, it can be used to visually determine the gradient of the jumping height in regards to the design parameters, and shows that the optimal results should occur around a 4000 N/m spring constant and the minimum damping ratio. \todo[inline]{something about how this can be used to visually instect the learned parameters.}

@@

\section{Learning Rate}
\label{app:lr_changes}

\begin{figure*}[tb]
\centering
\begin{minipage}[b]{.45\textwidth}
        \includegraphics[width=\linewidth]{figures/comp_learning_rate/avg_rew_ppo.png}
        \caption{PPO Reward}\label{label-a}
\end{minipage}
\hfill
\begin{minipage}[b]{.45\textwidth}
        \includegraphics[width=\linewidth]{figures/comp_learning_rate/avg_rew_td3.png}
        \caption{TD3 Reward}\label{label-b}
\end{minipage}
\end{figure*}

In the process of this project the effects of learning rate on the PPO and TD3 Algorithms were explored.
Figures~\ref{label-a} and \ref{label-b} show that the Time Steps needed for the PPO algorithm to converge is very sensitive to the choice in learning rate, it also shows
that the overall mean and standard deviation of the rewards is sensitive. On the other hand, Td3 does not appear to be at all sensitive to changes in the learning rate, at least not in the range
of learning rates explored in this study.

>>>>

The RL algorithm was utilized to find designs for two different reward cases. Time series data was captured during the simulation phase of training and was used to evaluate the designs performance through these rewards. The first reward case used was:
%
\begin{equation}
        \mathbb{R}_1 = \left (\textbf{X}  \right )_{\text{max}}
\end{equation}
% 
where $\textbf{X}$ was the timeseries rod height of the monopode captured during simulation. The goal of the first reward was to find a design that would cause the monopode to jump as high as possible.

The reward for the second case was:
%
\begin{equation}
        \mathbb{R}_2 = - \frac{\left (\textbf{X}  \right )_{\text{max}} - x_{s}}{x_{s}}
\end{equation}
%
where $x_s$ was the desired jump height, which was set to 0.1~m. The second case was utilized to test RL's ability to find a design that minimized the error between the maximum height reached and the desired maximum height to reach.

@@

Figures~\ref{fig:spring_zeta_height} represents the height the monopode could reach for the design/action space. The design space provided represents a space where a wider range of damping ratios are allowed. This wider range of possible values makes it more likely that the agent will settle to a local maxima. Additionally, it can be used to visually determine the gradient of the jumping height in regards to the design parameters, and shows that the optimal results should occur around a 4000 N/m spring constant and the minimum damping ratio.

@@

\section{Learning Rate}
\label{app:lr_changes}
\begin{figure}[tb]
\begin{center}
        \includegraphics[width=3in]{figures/comp_learning_rate/avg_rew_ppo.png}
        \caption{Reward Due to Changes in N Steps}
        \label{fig:ppo_rew}
\end{center}
% \vspace{-4mm}
\end{figure}

\begin{figure}[tb]
\begin{center}
        \includegraphics[width=3in]{figures/comp_learning_rate/avg_rew_td3.png}
        \caption{Reward Due to Changes in N Steps}
        \label{fig:td3_rew}
\end{center}
% \vspace{-4mm}
\end{figure}

In the process of this project the effects of learning rate on the PPO and TD3 Algorithms were explored.
Figures~\ref{fig:ppo_rew} and \ref{fig:td3_rew} show that the Time Steps needed for the PPO algorithm to converge is very sensitive to the choice in learning rate, it also shows that the overall mean and standard deviation of the rewards is sensitive. On the other hand, Td3 does not appear to be at all sensitive to changes in the learning rate, at least not in the range of learning rates explored in this study.
